Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 colt.tex
changes to COLT
finished edits up to payment
almost finished regret proof
added a new discussion tex file
halfway through editing payment proof
cleaned up and tightened technical lemmas
addressed some comments
pass through regret proof
Separating out a file for the abstract
drafted an abstract

\documentclass[twoside,11pt]{article}
\usepackage{jmlr2e}

@@

\usepackage[]{algorithm}
\usepackage[]{algorithmic}

\usepackage[utf8]{inputenc} % allow utf-8 input
%\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{xr} 
\usepackage{url}            % simple URL typesetting
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
%\usepackage{amsthm}
\usepackage{comment}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{float}
\usepackage{bbm}

\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
\usepackage{mathtools}

\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}

\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}

@@

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

@@

\title{Incentivizing Exploration with Heterogeneous Utilities}

\author{\name Bangrui Chen \email bc496@cornell.edu \\
\name Peter I.\ Frazier \email pf98@cornell.edu \\
\addr Operations Research and Information Engineering\\
Cornell University\\
New York, NY 14850, USA
\AND
\name David Kempe \email david.m.kempe@gmail.com  \\
\addr Department of Computer Science\\
University of Southern California\\
Los Angeles, CA 90089, USA}

@@

\begin{abstract}
sdafsd
\end{abstract}

\begin{keywords}
Incentivizing Exploration
\end{keywords}

\input{introduction.tex}

\input{problem_setting.tex}

\input{algorithm.tex}

\input{lower_bound.tex}

\input{conclusion.tex}

@@

\input{appendix.tex}

\vskip 0.2in

>>>>

\documentclass[twoside,11pt]{article}
\usepackage[anon]{jmlr2e}

@@

\usepackage[]{algorithm}
\usepackage[noend]{algorithmic}

%\usepackage[utf8]{inputenc} % allow utf-8 input
%\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage{microtype}      % microtypography
%\usepackage{xr}

\usepackage{url}            % simple URL typesetting
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
%\usepackage{amsthm}
%\usepackage{mathtools}

%\usepackage{comment}
%\usepackage{subcaption}
%\usepackage{xcolor}
%\usepackage{float}
\usepackage{bm}
\usepackage{bbm}
\usepackage{ifthen}
\usepackage{xspace}

\usepackage{color-edits}
% home-made package by David that provides the following macros:
% 1. \pfedit{}: prints argument in blue
% 2. \pfcomment{}: prints argument in blue in [Peter: #1]
% 3. \pfmargincomment{}: prints argument in blue in the margin as
% [Peter: #1]
% 4. \pfdelete{}: instead of text, marks a note in the margin in blue that says
% "Peter deleted here"
% Package has option [suppress], which gets rid of all color and all comments
% and [showdeletions], which shows deleted text in color/strikeout.
\addauthor[Peter]{pf}{blue}
\addauthor[Bangrui]{bc}{green}
\addauthor[David]{dk}{red}

%\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
%\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}

\providecommand{\SET}[1]{\ensuremath{\{ #1 \}}\xspace}
\providecommand{\Abs}[1]{\ensuremath{| #1 |}\xspace}
\providecommand{\Set}[2]{\ensuremath{\SET{#1 \mid #2}}\xspace}

\providecommand{\PROB}{\ensuremath{{\rm Prob}}\xspace}
\providecommand{\Prob}[2][]{\ensuremath{%
\ifthenelse{\equal{#1}{}}{\PROB\left[#2\right]}{\PROB_{#1}\left[#2\right]}}\xspace}
\providecommand{\ProbC}[3][]{\Prob[#1]{#2\;|\;#3}}
\providecommand{\Expect}[2][]{\ensuremath{%
\ifthenelse{\equal{#1}{}}{\mathbb{E}}{\mathbb{E}_{#1}}%
\left[#2\right]}\xspace}
\providecommand{\ExpectC}[3][]{\Expect[#1]{#2\;|\;#3}}

\newcommand{\e}{\mathrm{e}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\quarter}{\ensuremath{\frac{1}{4}}\xspace}

\providecommand{\Kth}[1]{\ensuremath{{#1}^{\rm th}}}

\def\QED{{\phantom{x}} \hfill \ensuremath{\rule{1.3ex}{1.3ex}}}

\newcommand{\extraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
\def\endextraproof{\QED \endtrivlist}

\def\emptyproof{\rm \trivlist \item[\hskip \labelsep{\bf Proof. }]}
\def\endemptyproof{\endtrivlist}

\newenvironment{rtheorem}[3][]{

\bigskip

\noindent \ifthenelse{\equal{#1}{}}{\bf #2 #3}{\bf #2 #3 (#1)}
\begin{it}
}{\end{it}}

\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
\newcommand{\R}{\mathbb{R}} % real numbers

@@

\input{localdefs}

@@

\title{Incentivizing Exploration by Heterogeneous Users}
% {Incentivizing Exploration with Heterogeneous Utilities}

%\author{\name Bangrui Chen \email bc496@cornell.edu \\
%\name Peter I.\ Frazier \email pf98@cornell.edu \\
%\addr Operations Research and Information Engineering\\
%Cornell University\\
%New York, NY 14850, USA
%\AND
%\name David Kempe \email david.m.kempe@gmail.com  \\
%\addr Department of Computer Science\\
%University of Southern California\\
%Los Angeles, CA 90089, USA}

@@

\begin{abstract}
\input{abstract.tex}
\end{abstract}

\begin{keywords}
Incentivizing Exploration, Multi-Armed Bandits
\end{keywords}

\input{introduction}

\input{problem_setting}

\input{result_discussion}

\input{algorithm}

\input{Discussion}

\input{lower_bound}

\input{conclusion}

@@

\input{payment-proof}

% \input{technical-proofs}
